---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Visualizing Smith STEM major requirements
The main function of the `smithscrapr` is to scrape some STEM major requirements from Smith College Website and turn them into data frames categorized by options. In other words, courses students have to take or choose to take to fulfill the major requirement. 

```{r setup}
library(smithscrapr)
```

Then, use the `req_df()` function to get data frames for each of the six majors, including Statistical and Data Sciences, Computer Sciences, Economics, Biochemistry, Astronomy, and Chemistry. The `major` argument should be "sds", "csc", "eco", "bch", "ast", or "chm". We input "sds" because we are retrieving the data frame for SDS major requirements. 

```{r}
sds <- req_df("sds")
sds
```

As you can see, to fulfill the SDS major, students must take every class for Capstone and Core, but they have the choice to choose one of the classes for the rest of the requirements, including Application, Communication, Programming, and Statistics.

The biology major is a special case because the requirements are different for each track. Use `bio_track_matcher()` to specify the track. We'll retrieve a data frame from track one, so we'll set the `track` argument to 1.

```{r}
track_one <- bio_track_matcher(1)
track_one
```

From above the students must take all the core courses in the list, choose one out of the two courses for fulfilling the chemistry and stats requirement, choose 3 200 or 300 level and 2 300 level courses to fulfil the upper level courses requirement, choose 2 electives, and take the lab courses under must and choose 2 200 or 300 level and 1 300 level courses to fullfil the lab requirement. 

## SDS Data

The `smithscrapr` package also comes with a built-in data set describing the major requirements for SDS.

```{r}
smithscrapr::sds_df
```

